Dark matter halo shapes in the Auriga simulations

### 2019-08-21 Document/paper.tex
edit

In our results we express the radius in units  of $R_{200}$ in
order to have a self-consistent dimensionless radial scale across all
halos. Given the similarity of the virial radii across halos, each dimensionless radius is
closely associated with a physical scale with a certain mean value and small standard deviation.
For instance, over the 30 halos in the sample, a dimensionless
radius of unity corresponds to a physical distance of $230\pm 16$
kpc.   Finally, we also measure the alignment of the halo shape against the
stellar disc angular momentum.  We measure the angular momentum vector 
using the $10\%$ oldest stellar particles within the virial radius.

@@

In the DMO sample, we find that halos become rounder with increasing radius.
The upper panels in Figure \ref{fig:slices} illustrate this effect.
The contours show a projected DM slice while the ellipsoid corresponds
to the full 3D shape determination. There we see a highly ellipsoidal halo shape at radii $\sim 3$ kpc
that becomes less elongated at $\approx 50$ kpc.

>>>>

In our results we express the radius in units  of $R_{200}$ in
order to have a self-consistent dimensionless radial scale across all
halos. Given the similarity of the virial radii across halos, each dimensionless radius is
closely associated with a physical scale with a certain mean value and small standard deviation.
For instance, over the 30 halos in the sample, a dimensionless
radius of unity corresponds to a physical distance of $230\pm 16$
kpc.   Finally, we also measure the alignment of the halo shape against the
stellar disc angular momentum measured using the $10\%$ oldest stellar
particles within the virial radius.

@@

In the DMO sample, we find that halos become rounder with increasing radius.
The upper panels in Figure \ref{fig:slices} illustrate this effect.
The contours show a projected DM slice while the ellipsoid corresponds
to the full 3D shape determination. There we see a highly ellipsoidal
halo shape at radii $\approx 3$ kpc that becomes less elongated at
$\approx 50$ kpc.
